---
title: 'Debugger in a knited doc'
output: html_document
---


```{r label='internal-setup', include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```


Try using the R package
[subprocess](https://cran.r-project.org/package=subprocess) to run some code
in a seperate R session.  The following example has been built using code
snippets provided in the 'intro' vignette from the subprocess package and the
example provided in the help file for `debugger`.

The first thing we will do is build a function for calling the R binary.


```{r label="setup_subprocess"}
library(subprocess)

R_binary <- function () {
  R_exe <- ifelse (tolower(.Platform$OS.type) == "windows", "R.exe", "R")
  return(file.path(R.home("bin"), R_exe))
}
```


Spawning a child R process is done as follows:


```{r label="spawning"}
child_r <- subprocess::spawn_process(R_binary(), c("--vanilla"))
Sys.sleep(2) # allow sufficient time for the child R process to start
subprocess::process_read(child_r)$stdout
```


We will write some code as a character string and send it to the child
process.


```{r }
unlink("testdump.rda")
code <-
'
options(error = quote(dump.frames("testdump", TRUE)))

f <- function() {
  g <- function() stop("test dump.frames")
  g()
}
f()   # will generate a dump on file "testdump.rda"
options(error = NULL)
'

invisible(subprocess::process_write(child_r, code))
subprocess::process_read(child_r)$stdout
```


Now, you can load the dump into the child process and start the debugger.

```{r }
code <-
'
load("testdump.rda")
debugger(testdump)
'
invisible(subprocess::process_write(child_r, code))
subprocess::process_read(child_r)$stdout
```


Say you want to start walking through the debugger for `f(1)`

```{r }
invisible(subprocess::process_write(child_r, "1\n"))
subprocess::process_read(child_r)$stdout
```


You can continue to walk through the debugging as needed via the child
process.

Don't forget to terminate the process

```{r }
subprocess::process_terminate(child_r)
```

