---
title: "Answer for SO Question 50879745"
header-includes:
  \usepackage{subcaption}
  \usepackage{booktabs}
  \usepackage[table]{xcolor}
---


```{r start-block}
library(dplyr)
library(knitr)
library(kableExtra)
opts_chunk$set(echo = FALSE)
``` 

Build two example tables based on the `mtcars` data set.


```{r sample, results='asis'}
t1 <- kable(head(mtcars)[1:3], format = "latex", booktabs = TRUE) %>%  kable_styling(latex_options = c("striped"), font_size=5)
t2 <- kable(head(mtcars)[4:6], format = "latex", booktabs = TRUE) %>%  kable_styling(latex_options = c("striped"), font_size=5) 
```

Modify the tables to use the `subtable` environment and added labels and
captions.

```{r}
t1 <- gsub("\\begin{table}[H]", "\\begin{subtable}[b]{0.48\\linewidth}\n\\caption{\\label{tab:1a}This is Table 1 in the example, but now labeled with a (a).}\n", t1, fixed = TRUE)
t1 <- gsub("\\end{table}", "\\end{subtable}", t1, fixed = TRUE) 

t2 <- gsub("\\begin{table}[H]", "\\begin{subtable}[b]{0.48\\linewidth}\n\\caption{\\label{tab:1b}Shorter caption.}", t2, fixed = TRUE)
t2 <- gsub("\\end{table}", "\\end{subtable}", t2, fixed = TRUE) 
```

Place the tables into the document.

```{r, results = "asis"}
cat("",
    "\\begin{table}[!htb]",
    "\\centering",
    "\\caption{\\label{tab:tab1}Two tables, side-by-side.}",
    t1,
    t2,
    "\\end{table}",
    "",
    sep = "\n") 
```

Another example, start by reading in a rds file.


```{r table, results = "asis"}
tbl <- readRDS("table.RDS") #load file using the link "tbl"
cat(tbl)
```

A few modifications to Table~\ref{tab:comments-block} will be made so that we
can show the table twice in a `subtable`.

```{r table2_mod}
tbl <- gsub("\\begin{table}", "\\begin{subtable}[t]{0.48\\linewidth}", tbl, fixed = TRUE)
tbl <- gsub("\\end{table}", "\\end{subtable}", tbl, fixed = TRUE) 
```

Printing the tables works, see \ref{tab:tab3}, but there is overlap as the
tables are too wide.  Consider the `tabularx` package as a solution or an ad hoc
approach of changing the font size.

```{r, results = "asis"}
cat("",
    "\\begin{table}[!htb]",
    "\\centering",
    "\\caption{\\label{tab:tab3}Two tables, side-by-side.}",
    # "\\scriptsize",
    tbl,
    tbl,
    "\\end{table}",
    # "\\normalsize",
    "",
    sep = "\n") 
```

